---
title: "HW3"
author: "Jose Bermudez"
date: "1/21/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(reticulate)
use_python("/Users/jabermud/miniconda3/bin/python")

library(printr)
```

```{r}

data(mtcars)
help(mtcars)

head(mtcars)

aggregate(mpg ~ cyl, data=mtcars, mean)

aggregate(mpg ~ cyl + gear, data=mtcars, mean)

```

```{r}
library(dplyr)

results = mtcars %>%
  group_by(cyl) %>%
  summarise(mean_mpg = mean(mpg))

results

```

```{r}
results = mtcars %>%
  group_by(cyl, gear) %>%
  summarise(mean_mpg = mean(mpg))

as.data.frame(results)
```

## a working example

```{r, echo=FALSE}
if(file.exists("mtcars.sqlite3"))
{
  file.remove("mtcars.sqlite3")
}
```


```{r}

library(dbplyr)

con <- DBI::dbConnect(RSQLite::SQLite(), "mtcars.sqlite3")

DBI::dbWriteTable(con, "mtcars", mtcars)

DBI::dbDisconnect(con)

```

```{sh}
ls -lhrt *.sqlite3

```

```{r}
con <- DBI::dbConnect(RSQLite::SQLite(), "mtcars.sqlite3")
mtcars2 <- tbl(con, "mtcars")

g = mtcars2 %>%
  group_by(cyl) %>%
  summarise(mean_mpg=mean(mpg))

g %>% show_query()

result = g %>% collect()
as.data.frame(result)

```

## Python

```{r, echo=FALSE}
if(file.exists("mtcars_from_pandas.sqlite3"))
{
  file.remove("mtcars_from_pandas.sqlite3")
}

```{python}
mtcars = r.mtcars
mtcars.head()
```

```{python}
mtcars.groupby(['cyl'])['mpg'].mean()

mtcars.groupby(['cyl', 'gear'])['mpg'].mean()

```

```{python}
import sqlite3 
con = sqlite3.connect("mtcars_from_pandas.sqlite3")
mtcars.to_sql("mtcars", con)
con.close()

```

```{sh}
ls -lhrt *.sqlite3
```


```{python}
import pandas as pd

con = sqlite3.connect("mtcars_from_pandas.sqlite3")
df = pd.read_sql("select * from mtcars", con)
df.head()
```

```{python}
df = pd.read_sql("select cyl, avg(mpg) from mtcars group by cyl", con)
df.head()
```

```{python}
df = pd.read_sql("select cyl, gear, avg(mpg) from mtcars group by cyl, gear", con)
df.head()
```
